There once was a grid at ol' Carkeek

### 2016-04-13 Manuscript/v0.0/carkeek_grid.tex
add text on relationship between distance and dissimilarity

\usepackage[T1]{fontenc} % Choose an output font encoding (T1) that has support for the accented characters used by the most widespread European languages
\usepackage[utf8]{inputenc} % Allow input of accented characters (and more...)
\usepackage{graphicx} %  figures
\usepackage[round]{natbib} % names in citations
\usepackage{lineno} % line numbers
\usepackage{authblk} % allows more intuitive formatting for multiple authors/affiliations
\usepackage[margin=1in]{geometry} % make the margins 1 inch on all sides of the document
%\usepackage{amsmath} % useful for formatting math stuff, especially complex equations
%\usepackage{pdflscape} % rotate table into landscape mode
%\usepackage{subfigure} % side by side figures
%\usepackage{longtable} % for tables that span multiple pages.
\usepackage{setspace} % double spacing

@@

@@

We assessed PCR contamination by evaluating the dissimilarity of replicate PCRs of the same DNA sample, and removed one sample for which the Bray-Curtis dissimilarities between itseld and the other replicates exceeded 0.1 (lib\_B\_tag\_GCGCTC).

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/comm_diss_by_geo_dist.pdf}
    \caption{Pairwise Bray-Curtis dissimilarity of eDNA communities plotted against pairwise spatial distance.}
  \label{comm_diss_by_geo_dist} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

>>>>

\usepackage[T1]{fontenc} % Choose an output font encoding (T1) that has support for the accented characters used by the most widespread European languages
\usepackage[utf8]{inputenc} % Allow input of accented characters (and more...)
\usepackage{textcomp,marvosym} % additional figures, including textdegree
\usepackage{graphicx} %  figures
\usepackage[round]{natbib} % names in citations
\usepackage{lineno} % line numbers
\usepackage{authblk} % allows more intuitive formatting for multiple authors/affiliations
\usepackage[margin=1in]{geometry} % make the margins 1 inch on all sides of the document
%\usepackage{amsmath} % useful for formatting math stuff, especially complex equations
%\usepackage{pdflscape} % rotate table into landscape mode
%\usepackage{subfigure} % side by side figures
%\usepackage{longtable} % for tables that span multiple pages.
\usepackage{setspace} % double spacing

@@

% We measure 'extra-(corporeal|organismal) DNA
Some authors have cautioned against the use of DNA-based macrobial communities in marine environments because they are subject to dynamic physical forces (CITE).
If environmental circulation 
In general, the relationship between community dissimilarity (0 = identical; 1 = completely different) and spatial distance is expected to be asymptotic, because communities nearer to each other tend to be more similar than those farther apart.
The intercept is expected to be near 0, because samples taken at the same place should be very similar. % technically impossible for samples to be taken at exactly 0; they are actually immediately adjacent.
Deviation in the intercept from 0 indicates heterogeneous community composition/structure over fine scales.
A flat relationship between dissimilarity and distance indicates that heterogeneity is not assorted spatially, and can be interpreted in different ways, depending on the mean.
If the mean is near 1, the spatial heterogeneity has overwhelmed the spatial scale of sampling.
If the mean is near 0, there is no community heterogeneity over the scale sampled.

@@

We assessed PCR contamination by evaluating the dissimilarity of replicate PCRs of the same DNA sample, and removed one sample for which the Bray-Curtis dissimilarities between itself and the other replicates exceeded 0.1 (lib\_B\_tag\_GCGCTC).

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/diss_by_dist.pdf}
    \caption{Pairwise Bray-Curtis dissimilarity of eDNA communities plotted against pairwise spatial distance.
    Line represents prediction of Gaussian LOESS (degree = 1; span = 2/3).
    Restricting comparison to within-transect has no qualitative difference in the outcome (see 'diss\_by\_dist\_by\_transect.pdf').
    }
  \label{comm_diss_by_geo_dist} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}
